Beef Pricing Dynamics in Canadian Supermarkets

### 2024-12-03 paper/paper.qmd
Add files via upload

The summary shows that the current_price in the dataset ranges from 0.39 to 101.15, with most prices concentrated in the lower range, as indicated by a median of 6.87 and a third quartile of 10.99. The average price is 9.56, while the standard deviation of 11.39 suggests significant variability, likely influenced by a few high outliers.
```{r}
#| label: tbl-summary
#| fig-cap: Summary Statistics for Current Price
#| echo: false

>>>>

The summary shows that the current price in the dataset ranges from 0.39 to 101.15, with most prices concentrated in the lower range, as indicated by a median of 6.87 and a third quartile of 10.99. The average price is 9.56, while the standard deviation of 11.39 suggests significant variability, likely influenced by a few high outliers.
```{r}
#| label: tbl-summary
#| fig-cap: Summary Statistics for Current Price
#| echo: false
